Experience Report: Haskell in Computational Biology

### 2012-07-01 mrfy_experience_report.tex
problems with parallelism

We~also found an opportunity to improve performance through parallelism.
Calls on query sequences between beta strands are independent,
as are calls on different placements.
We~found them easy to parallelize
using
\texttt{Control.Parallel}:
we substituted
\texttt{parmap rseq} for \texttt{map}.
We have access to a
one 48-core, 2.3GHz AMD Opteron 6176 system, on which we benchmarked \mrfy\ performing
a search on a large protein structure (an ``8-bladed beta-propeller'')
comprising 343 hidden Markov model nodes and 40 beta strands, and a query sequence
592 amino acids long.
Figure~\ref{multicore} illustrates the mean speedup \mrfy\ achieves as the number of
processing cores increases.
Optimal speedup appears to occur between 12 and 16 processors.

@@

\begin{figure}[h!]
\centerline{\includegraphics{speedup}}
\bigskip
\caption{\mrfy's parallel speedup}
\label{fig:speedup}
\end{figure}

\begin{figure}[h!]
\centerline{\includegraphics{efficiency}}
\bigskip
\caption{\mrfy's parallel efficiency}
\label{fig:efficiency}
\end{figure}

@@

>>>>

We~also found an opportunity to improve performance through parallelism.
Calls on query sequences between beta strands are independent,
as are calls on different placements.
We~found them easy to parallelize
using
\texttt{Control.Parallel}:
we substituted
\texttt{parmap rseq} for \texttt{map}.
On a 48-core, 2.3GHz AMD Opteron 6176 system, 
parallel performance is good up to about 12~cores.
\figref{fig:efficiency} shows parallel efficiency when
using a model of an ``8-bladed beta propeller;''
the model has 343 ordinary nodes and 40~beta strands TOTALLING HOW
MANY NODES?
We~benchmarked \mrfy\ using a query sequence of
592 amino acids.
Figure~\ref{fig:speedup} SHOWS NOTHING OF VALUE BECAUSE RANDOMNESS
BREAKS EVERYTHING.  AND IT SHOULD HAVE ERROR BARS.
(Parallel efficiency is 1.0 when the speedup is equal to the number of cores
used.
Lower speedups mean lower efficiency.)

@@

\begin{figure}%%%[h!]
\centerline{\includegraphics{efficiency}}
\bigskip
\caption{\mrfy's WRONG parallel efficiency}
\label{fig:efficiency}
\end{figure}

@@

\break

\begin{figure}%%%[h!]
\centerline{\includegraphics{speedup}}
\bigskip
\caption{\mrfy's parallel speedup}
\label{fig:speedup}
\end{figure}
